Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-08-09 analysis/report/effectiveness_report.Rmd
update report

```{r flowchart, echo=FALSE}

@@

print_plots <- function(outcome, outcome_descr){
  km_image <- here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.png"))
  calendar_image <- here("output", outcome, "calendar", glue("effect_plot.png"))
  timesincevax_image <- here("output", outcome, "timesincevax", glue("effect_plot.png"))

  km_plot <- read_rds(here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.rds")))
  km_plot <- km_plot + theme(legend.position = c(0.1,0.1), legend.justification = c(0,0))

  calendar_effects <- read_rds(here("output", outcome, "calendar", glue("effect_estimates.rds"))) %>%
    mutate(timescale = "Calendar time")
  timesincevax_effects <- read_rds(here("output", outcome, "timesincevax", glue("effect_estimates.rds"))) %>%
    mutate(timescale = "Vaccinated time")

  effects <- bind_rows(calendar_effects, timesincevax_effects)

  effects_plot <-
    ggplot(data = effects) +
    geom_point(aes(y=estimate, x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_linerange(aes(ymin=conf.low, ymax=conf.high, x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_hline(aes(yintercept=1), colour='grey')+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(breaks=unique(effects$term_left), limits=c(min(effects$term_left), max(effects$term_right)+1), expand = c(0, 0))+
    scale_y_log10(
    breaks=c(0.1, 0.125, 0.25, 0.33, 0.5, 0.75, 1, 1.33, 2, 3, 4, 8,10),
    sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
  )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=2))+
    labs(
      y="Hazard ratio",#\nChAdOx1 / BNT162b2",
      x="Days since vaccination",
      colour=NULL
     ) +
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  # 
  # calendar_plot <- read_rds(here("output", outcome, "calendar", glue("effect_plot.rds"))) + 
  #   labs(title=NULL)+
  #   coord_cartesian(ylim=c(0.25,4))+
  #   theme(text = element_text(size=10))
  # 
  # timesincevax_plot <- read_rds(here("output", outcome, "timesincevax", glue("effect_plot.rds"))) + 
  #   labs(title=NULL)+
  #   coord_cartesian(ylim=c(0.25,4))+
  #   theme(text = element_text(size=10))
  # 
  #cat(glue("### {outcome_descr}"), "  \n")

  #effects_plot <- wrap_plots(calendar_plot, timesincevax_plot, nrow=1)#, guides='collect')
  cat("  \n\n")
  print(glue("### {outcome_descr}"), "  \n")
  print(km_plot)
  print(effects_plot)
  cat("  \n\n")
  # wrap_plots(
  #  km_plot + labs(title=outcome_descr),
  #  effects_plot,
  #  ncol=1
  # ) +
  # plot_annotation(title = outcome_descr)

print_plots("test", "SARS-CoV-2 test")
print_plots("postest", "SARS-CoV-2 positive test")
print_plots("emergency", "A&E attendance")
print_plots("covidadmitted", "COVID-19 hospital admission")
#print_plots("covidcc", "COVID-19 critical care admission")

>>>>

```{r flowchart, echo=FALSE, warning=FALSE, message=FALSE}

@@

print_plots_km <- function(outcome){

  km_image <- here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.png"))

  km_plot <- read_rds(here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.rds")))

  print(km_plot)
  cat("  \n\n")

print_plots_effects <- function(outcome, modeltype){

  suffix <- if(modeltype=="plr"){
    "_pw"
  } else{
    ""
  }

  calendar_effects <- read_rds(here("output", "models", outcome, "calendar", glue("report{modeltype}_effects{suffix}.rds"))) %>%
    mutate(timescale = "Calendar time")
  timesincevax_effects <- read_rds(here("output", "models", outcome, "timesincevax", glue("report{modeltype}_effects{suffix}.rds"))) %>%
    mutate(timescale = "Vaccinated time")

  tidy_effects <- bind_rows(calendar_effects, timesincevax_effects)

  plot_effects <-
    ggplot(data = tidy_effects) +
    geom_point(aes(y=exp(estimate), x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_linerange(aes(ymin=exp(conf.low), ymax=exp(conf.high), x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_hline(aes(yintercept=1), colour='grey')+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(breaks=unique(tidy_effects$term_left), limits=c(min(tidy_effects$term_left), max(tidy_effects$term_right)+1), expand = c(0, 0))+
    scale_y_log10(
    breaks=c(0.1, 0.125, 0.25, 0.33, 0.5, 0.75, 1, 1.33, 2, 3, 4, 8,10),
    sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
  )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=2))+
    labs(
      y="Hazard ratio",#\nChAdOx1 / BNT162b2",
      x="Days since vaccination",
      colour=NULL
     ) +
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  print(plot_effects)
  cat("  \n\n")
}

cat("  \n\n")
print(glue("### SARS-CoV-2 test"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("test")
print(glue("#### Cox"), "  \n")
print_plots_effects("test", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("test", "plr")

cat("  \n\n")
print(glue("### SARS-CoV-2 positive test"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("postest")
print(glue("#### Cox"), "  \n")
print_plots_effects("postest", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("postest", "plr")

cat("  \n\n")
print(glue("### A&E attendance"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("emergency")
print(glue("#### Cox"), "  \n")
print_plots_effects("emergency", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("emergency", "plr")

cat("  \n\n")
print(glue("### COVID-19 hospital admission"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("covidadmitted")
print(glue("#### Cox"), "  \n")
print_plots_effects("covidadmitted", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("covidadmitted", "plr")
